`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2016-09-11 inst/manuscript/manuscript.rmd
Fix typos;

# Keywords
scramblase; sithionite scramblase assay; R

@@

`flippant`'s capabilities are demonstrated here by reanalyzing a subset of the
data underlying Figure 4C--F in @ploier_dimerization_2016. The first step is to
extract the data files, stored in a ZIP archive within the pacakge.

@@

## Availability of data and material
Upon acceptance of the manuscript, `flippant` will be depositied as a
self--contained `R` package including all data presented in the `Bioconductor`
collection of tools for biomedical data analysis [@huber_orchestrating_2015].

>>>>

# Keywords
scramblase; dithionite scramblase assay; R

@@

`flippant`'s capabilities are demonstrated here by reanalyzing a subset of the
data underlying Figure 4C--F in @ploier_dimerization_2016. The first step is to
extract the data files, stored in a ZIP archive within the package.

@@

## Availability of data and material
Upon acceptance of the manuscript, `flippant` will be deposited as a
self--contained `R` package including all data presented in the `Bioconductor`
collection of tools for biomedical data analysis [@huber_orchestrating_2015].
